\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

This thesis was made possible by the continuous support of family and friends that always encouraged me and believed on my ability to reach ambitious goals.
%
The journey that led to this work started in Lisbon, together with eight wonderful colleagues, all eager to embark on a PhD in plasma physics, the second cohort (C2) of the APPLAuSE doctoral program, Adwiteey, Anton, Giannandrea, Hugo, Marija, Rolando, Thomas Wodzinski and Thomas Greenslade.
%
I would like to thank all of C2 for their support, and Prof. Luís Lemos Alves, Prof. Carlos Silva and Prof. Bruno Gon\char231 alves to invite me to be part of this challenging doctoral program.
%
In Lausanne, I was able to meet fantastic people, from students to professors, that really made me step to the next level.
%
I am grateful to my office mates during these years, Anna, Dahye, Federico, Hugo, Jeremy, Matteo, Maurizio,  and Roberto, to the friends I made during my Masters that helped me perform the transition to Switzerland, Madhu, and Andreas, to the portuguese crew, André, Eduardo, Miguel and Phillip, and to all my fellow colleagues at SPC, PhD students, post-docs and scientists.
%
Regarding the people I worked with directly, I am grateful to Stephan Brunner, for enlightening me on several important aspects of plasma physics theory, and to the students Antoine Baillod, Baptiste Frei, Lorenzo Perrone, Sonia Gamba, and Konovets Vyacheslav for their perseverance, hard work, and important contributions to this thesis.

I would like to express my gratitude to my advisors Prof. Paolo Ricci and Prof. Nuno Loureiro.
%
The partnership between the three of us has endured for more than five years, and has resulted not only on this thesis and a number of publications, but it also allowed me to expand my knowledge and, in general, to become a better physicist.
%
For their patience and motivation, I am extremely grateful.
%
Finally, a very special word to Sandra Paiva, who was present when I most needed her, for which this thesis  and my time in Switzerland would have looked much different without her support, and to my family, that always gave me the best advice and allowed all this to be possible.

%\noindent\textit{Lausanne, 10 January 2019}
%\hfill R.~K.
